Cleaning AMP data

```{r}
library(tidyverse)
#Change to your own directory (where you keep the data file)
getwd()
#dir = 'C:\\Users\\yoav\\Documents\\bigfiles\\qualtrics.iat\\gal.elinor\\raw'
df <- read.csv("AMP_data_21_01.csv")
df1 <- as.data.frame(df[3:9,])

write.csv(df1, file = "amp_data.csv")
colnames(df1)[1] <- "amp"
df2 <- separate(df1, amp,into= ,sep = ",")
```

```{r}
# Copied from Elad Zlotnick (from here: https://github.com/eladzlot/minnojs-qiat/blob/master/qiat.R)
# Parse csv generated by minnoJS
#
# @param df a data frame
# @param id the column name holding the ids
# @param data the column name holding the data (we assume the data holds an array of unnested objects)
#
# @example
# qiat.parse.quoted(df, 'ResponseId', 'Q_47')
# qiat.parse(df, ResponseId, Q_47)
#
# @returns data frame with parsed data, rows with NA or '' are omitted.
qiat.parse.quoted = function(df, ResponseId, data){
  # @TODO does not work?
  # if (is.factor(df[id])) stop(paste0(data, ' column must not be a factor'))
  filteredDF = df[df[,data]!='' & !is.na(df[,data]) ,]
  
  # parse data -> list of data data frames
  csvList = lapply(filteredDF[,data], function(str) tryCatch({
    read.csv(text=str,stringsAsFactors = FALSE)
  },
  error = function(err){
    message('woa there is a malformed csv here')
    return(NA)
  }
  ))
  #browser()
  # add id to each data DF
  mask = which(sapply(csvList,nrow)>0)
  dataPages = mapply(
    function(id, df) cbind(id,df),
    filteredDF[mask,id],
    csvList[mask],
    SIMPLIFY = FALSE
  )
  
  if (!length(dataPages)) { return(data.frame()) }
  
  # concat pages
  do.call(rbind,dataPages)
}